\tcode{Generalisation of nth_element to a range of nths}

### 2021-12-28 draft_lundberg_nth_elements.tex
iterator_t, iter_reference_t instead of declval, decltype. Typo

\begin{codeblock}
template< class RandomAccessIterator, class RandomAccessIterator2 >
constexpr void @\textbfx{multi_nth_element}@(RandomAccessIterator first, 
  RandomAccessIterator2 nth_first, RandomAccessIterator2 nth_last, 
  RandomAccessIterator last)
{
  if (last - first <= 32) { @\textbfx{std::sort(first, last)}@; return; }
  const auto nth_dist = nth_last - nth_first;
  if (nth_dist == 0 || *nth_first == last) return;
  const auto nth_mid = nth_first + nth_dist / 2;
  const auto at_nth_mid = *nth_mid;
  @\textbfx{nth_element(first, at_nth_mid, last)}@;
  @\textbfx{multi_nth_element(first, nth_first, nth_mid, at_nth_mid)}@;
  if (at_nth_mid != last){
    const auto nth_left = std::upper_bound(nth_mid, nth_last, at_nth_mid );
    @\textbfx{multi_nth_element(at_nth_mid + 1, nth_left, nth_last, last)}@;
  }
}

@@

\pnum
\expects
\range{first}{nth} and \range{nth}{last} are valid ranges.
For the overloads in namespace \tcode{std},
\tcode{RandomAccessIterator} meets
the \oldconcept{ValueSwappable} requirements\iref{swappable.requirements}, and
the type of \tcode{*first} meets
the \oldconcept{MoveConstructible} (\tref{cpp17.moveconstructible}) and
\oldconcept{MoveAssignable} (\tref{cpp17.moveassignable}) requirements.
\added{For the overloads taking a range [nths_first,nths_last), RandomAccessIterator2 is a \oldconcept{RandomAccess} iterator, and *nths_first is convertible to  RandomAccessIterator. For every iterator i and j in the range [nths_first,nths_last), it holds that if \tcodeadd{i<j} then \tcodeadd{!(*j<*i).}}

@@

\begin{codeblockAdd}
template<class RandomAccessIterator, class RandomAccessIterator2>
constexpr void nth_element(
RandomAccessIterator first, 
RandomAccessIterator2 nths_first, RandomAccessIterator2 nths_last,
RandomAccessIterator last);

template<class RandomAccessIterator, class RandomAccessIterator2, class Compare>
constexpr void nth_element(
RandomAccessIterator first, 
RandomAccessIterator2 nths_first, RandomAccessIterator2 nths_last,
RandomAccessIterator last, Compare comp);
\end{codeblockAdd}
\newpage
\begin{codeblockAdd}
template<class ExecutionPolicy, class RandomAccessIterator, class RandomAccessIterator2>
void nth_element(ExecutionPolicy&& exec,
RandomAccessIterator first, 
RandomAccessIterator2 nths_first, RandomAccessIterator2 nths_last,
RandomAccessIterator last);

template<class ExecutionPolicy, class RandomAccessIterator,
class RandomAccessIterator2, class Compare>
void nth_element(ExecutionPolicy&& exec,
RandomAccessIterator first, 
RandomAccessIterator2 nths_first, RandomAccessIterator2 nths_last,
RandomAccessIterator last, Compare comp);

@@

\begin{codeblockAdd}
namespace ranges {
  template<@\libconcept{random_access_iterator}@ I, @\libconcept{sentinel_for}@<I> S,
  random_access_range R2, class Comp = ranges::less, class Proj = identity>
  requires @\libconcept{sortable}@<I, Comp, Proj>
  && std::convertible_to<decltype(*std::declval<R2>().begin()), I>
  constexpr I nth_element(I first, I nth, S last, Comp comp = {}, Proj proj = {});

  template<@\libconcept{random_access_range}@ R,
  random_access_range R2, class Comp = ranges::less, class Proj = identity>
  requires @\libconcept{sortable}@<iterator_t<R>, Comp, Proj>
  && std::convertible_to<decltype(*std::declval<R2>().begin()), 
   decltype(std::declval<R>().begin())> 
  constexpr borrowed_iterator_t<R> 
  nth_element(R&& r, iterator_t<R> nth, Comp comp = {}, Proj proj = {}); 
}

>>>>

\begin{codeblock}
template< class RandomAccessIterator, class RandomAccessIteratorNths >
constexpr void @\textbfx{multi_nth_element}@(RandomAccessIterator first, 
  RandomAccessIteratorNths nth_first, RandomAccessIteratorNths nth_last, 
  RandomAccessIterator last)
{
  if (last - first <= 32) { @\textbfx{std::sort(first, last)}@; return; }
  const auto nth_dist = nth_last - nth_first;
  if (nth_dist == 0 || *nth_first == last) return;
  const auto nth_mid = nth_first + nth_dist / 2;
  const auto at_nth_mid = *nth_mid;
  @\textbfx{nth_element(first, at_nth_mid, last)}@;
  @\textbfx{multi_nth_element(first, nth_first, nth_mid, at_nth_mid)}@;
  if (at_nth_mid != last){
    const auto nth_left = std::upper_bound(nth_mid, nth_last, at_nth_mid );
    @\textbfx{multi_nth_element(at_nth_mid + 1, nth_left, nth_last, last)}@;
  }
}

@@

\pnum
\expects
\range{first}{nth} and \range{nth}{last} are valid ranges.
For the overloads in namespace \tcode{std},
\tcode{RandomAccessIterator} meets
the \oldconcept{ValueSwappable} requirements\iref{swappable.requirements}, and
the type of \tcode{*first} meets
the \oldconcept{MoveConstructible} (\tref{cpp17.moveconstructible}) and
\oldconcept{MoveAssignable} (\tref{cpp17.moveassignable}) requirements.
\added{For the overloads taking a range [nths_first,nths_last), RandomAccessIteratorNths is a \oldconcept{RandomAccess} iterator, and *nths_first is convertible to  RandomAccessIterator. For every iterator i and j in the range [nths_first,nths_last), it holds that if \tcodeadd{i<j} then \tcodeadd{!(*j<*i).}}

@@

\begin{codeblockAdd}
template<class RandomAccessIterator, class RandomAccessIteratorNths>
constexpr void nth_element( RandomAccessIterator first, 
RandomAccessIteratorNths nths_first, RandomAccessIteratorNths nths_last,
RandomAccessIterator last);

template<class RandomAccessIterator, class RandomAccessIteratorNths, class Compare>
constexpr void nth_element( RandomAccessIterator first, 
RandomAccessIteratorNths nths_first, RandomAccessIteratorNths nths_last,
RandomAccessIterator last, Compare comp);
\end{codeblockAdd}
\newpage
\begin{codeblockAdd}
template<class ExecutionPolicy, class RandomAccessIterator, class RandomAccessIteratorNths>
void nth_element(ExecutionPolicy&& exec, RandomAccessIterator first, 
RandomAccessIteratorNths nths_first, RandomAccessIteratorNths nths_last,
RandomAccessIterator last);

template<class ExecutionPolicy, class RandomAccessIterator,
class RandomAccessIteratorNths, class Compare>
void nth_element(ExecutionPolicy&& exec, RandomAccessIterator first, 
RandomAccessIteratorNths nths_first, RandomAccessIteratorNths nths_last,
RandomAccessIterator last, Compare comp);

@@

\begin{codeblockAdd}
namespace ranges {
  template<@\libconcept{random_access_iterator}@ I, @\libconcept{sentinel_for}@<I> S,
  @\libconcept{random_access_range}@ Nths, class Comp = ranges::less, class Proj = identity>
  requires @\libconcept{sortable}@<I, Comp, Proj>
  && @\libconcept{convertible_to}@<iter_reference_t<iterator_t<Nths>>, I>
  constexpr I nth_element(I first, Nths&& nths, S last, Comp comp = {}, Proj proj = {});

  template<@\libconcept{random_access_range}@ R,
  @\libconcept{random_access_range}@ Nths, class Comp = ranges::less, class Proj = identity>
  requires @\libconcept{sortable}@<iterator_t<R>, Comp, Proj>
  && @\libconcept{convertible_to}@<iter_reference_t<iterator_t<Nths>>, iterator_t<R>>
  constexpr borrowed_iterator_t<R> 
  nth_element(R&& r, Nths&& nths, Comp comp = {}, Proj proj = {}); 
}
